Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-28 JCB/methods_JCB.tex
Typo

In principle, $\Theta(m\cdot n^2)$ terms, identified by $(m,i,j)$ triplets, should be computed.
However, a close inspection of the recurrences reveals that the computation can be safely restricted to a subset of intervals $(i,j)$.
For instance, the inside algorithm only requires computing intervals $[i,j]$ that do not break any base-pair, and whose next position $j+1$ is either past the end of the sequence, or is base-paired prior to $i$. Similar constraints hold for the outside computation,  following from the linearity of the outside recurrence (i.e. the computation of the outside term for a given excluded structure only relies on the computation of another, strictly larger, structure).

>>>>

In principle, $\Theta(M\cdot n^2)$ terms, identified by different $(\Struct,m)$ triplets, should be computed.
However, a close inspection of the recurrences reveals that the computation can be safely restricted to a subset of intervals $(i,j)$.
For instance, the inside algorithm only requires computing intervals $[i,j]$ that do not break any base-pair, and whose next position $j+1$ is either past the end of the sequence, or is base-paired prior to $i$. A similar property holds for the outside computation,  following from the linearity of the outside recurrence (i.e. the computation of the outside term for a given excluded structure only relies on the computation of another, strictly larger, structure).

### 2013-05-28 JCB/results_JCB.tex

{\centering \url{https://github.com/McGill-CSB/RNApyro}\\}
\TODOJerome{Did we set up an ad hoc website?}

The time benchmarks were performed on a MacMini 2010, 2.3GHz dual-core Intel Core i5, 8GB of RAM.
Since typical use-cases of \RNApyro require
 efficiency and scalability, we present in TableFigure~\ref{fig:time} typical runtimes required to compute the probabilities for  every nucleotide at every positions for a vast set of parameters. For those tests,
 both the multiple sequence alignment and the reference sequence were generated uniformly at random, based on a realistic random secondary structure, generated as described in Levin~\emph{et al}~\cite{Levin:2012kx}.
\TODOVlad{Add more extensive time benchmark, as a plot}

>>>>

%{\centering \url{https://github.com/McGill-CSB/RNApyro}\\}
%\TODOJerome{Did we set up an ad hoc website?}

{\centering \url{http://csb.cs.mcgill.ca/RNApyro}\\}
The time benchmarks were performed on a MacMini 2010, 2.3GHz dual-core Intel Core i5, 8GB of RAM.
%on AMD Opteron(tm) Processor 6278  at 2.4 GHz with cache of 512 KB.20 cores and 175 GB ram.
Since typical use-cases of \RNApyro require efficiency and scalability, we present in TableFigure~\ref{fig:time}
typical runtimes required to compute the probabilities for  every nucleotide at every positions for a vast set of parameters.
For those tests, both the multiple sequence alignment and the reference sequence were generated uniformly at random,
based on a realistic random secondary structure, generated as described in Levin~\emph{et al}~\cite{Levin:2012kx}.
\TODOVlad{Add more extensive time benchmark, as a plot}
\TODOVlad{Is time benchmark still on Mac mini or mcbbigram?}
